## Response variables
 
```{r setup, include=FALSE, cache=FALSE}
#Set root directory to R project root
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r eval=FALSE}
library(tidyverse)
```


### BAM data

```{r readBAM, eval=FALSE}
BAM<-read.csv("0_data/external/BAM_ss_spp.csv", header = TRUE)
b<-BAM%>%
  filter(DATE!="")

# Prep data
# rename columns
names(b)[7]<- "x"
names(b)[8]<- "y"

#add source column
b$source<-"BAM"
#remove unneeded fields
b<-b[ -c(2)]

#Change myrtle warbler to yellow-rumped warbler
b$SPECIES[b$SPECIES == "MYWA"] <- "YRWA"


# Consolodate abundance estimates from duplicate stations
# ~ are the grouping variables while the . represents all other variables to sum  
b<-aggregate(. ~SS+DATE+TIME+MAXDUR+MAXDIS+x+y+surveyType+SPECIES+source, b, sum)

b$DATE<-as.Date(b$DATE)
# # change data class where needed. Need to match the classes of the columns in the other bird dataframes to merge.
# b$MAXDIS<-as.character(b$MAXDIS)
```


### WildTrax data

*See the wildRtrax article here for more details on authentication:* <https://abbiodiversity.github.io/wildRtrax/articles/authenticating-into-wt.html>

1.  **Load packages**

```{r eval=FALSE}

#install.packages("remotes")
remotes::install_github("ABbiodiversity/wildRtrax")

library(wildRtrax)
library(tidyverse)
library(lubridate)
library(hms)
```

2.  **Login to WildTrax**

NOTE: Edit the 'loginexample.R' script to include your WildTrax login details and rename to 'login.R'. DO NOT PUSH YOUR LOGIN TO GITHUB

```{r eval=FALSE}
config <- "1_code/r_scripts/login.R"
source(config)

wt_auth()
```

3.  **Get list of projects from WildTrax**

```{r eval=FALSE}
projects <- wt_get_download_summary(sensor_id = 'ARU')
```

4.  **Download multiple projects**

```{r eval=FALSE}

# list target projects
target<-c("381", "31", "161", "41", "73", "334", "600", "620", "592", "85", "10", "5", "1360", "1115", "80", "81", "82", "83", "361", "1360", "1115", "1884")
projects.test <- projects%>%
 filter(project_id %in% target)

dat.list <- list()
error.log <- data.frame()
for(i in 1:nrow(projects.test)){
  
  dat.list[[i]] <- try(wt_download_report(project_id = projects.test$project_id[i], sensor_id = projects.test$sensorId[i], weather_cols = F, report = "summary"))
  
  print(paste0("Finished dataset ", projects.test$project[i], " : ", i, " of ", nrow(projects.test), " projects"))
}

dat <- do.call(rbind, dat.list)
```

5.  **Save with metadata & timestamp**

```{r eval=FALSE}
save(dat, projects.test, error.log, file=paste0("0_data/manual/bird/wildtrax_raw_", Sys.Date(), ".rData"))
```

```{r}
w<-dat%>%
  filter(status=="Transcribed")%>%
  dplyr::rename(c(SS=location, x=longitude, y=latitude, SPECIES=species_code, ABUND=abundance))%>%
  mutate(source="WT")%>%
  mutate(surveyType="ARU")%>%
  mutate(MAXDIS="Inf")%>%
  mutate(MAXDIS=as.numeric(MAXDIS))%>%
  mutate(recording_date=lubridate::as_datetime(recording_date))%>%
  mutate(DATE=lubridate::date(recording_date))%>%
  mutate(TIME=format(as.POSIXct(recording_date), format = "%H:%M"))

#Change myrtle warbler to yellow-rumped warbler
w$SPECIES[w$SPECIES == "MYWA"] <- "YRWA"


w$MAXDUR <- as.numeric(gsub("s.*$", "", w$method))

w<-w%>%dplyr::select(c("SS","DATE","TIME","MAXDUR","MAXDIS","x","y", "surveyType", "SPECIES", "ABUND", "source", "individual_appearance_order"))%>%
  filter(ABUND!="N/A"&!grepl('CI', ABUND)&ABUND!="")
```

##### seperate numerical and "too many to count" abundance values {-}

```{r eval=FALSE}
w2<-w
#add new columns for abundance data (convert words to numbers)
w2$ABUND_TMTT[w2$ABUND=="TMTT"]<-"TMTT"

#Seperate dataframe by species with a numeric ABUND vs too many to count
w_TMTT<-filter(w2, w$ABUND=="TMTT")
#w_TMTT<- w_TMTT[-c(7:9)]
w_TMTT<- distinct(w_TMTT)

#filter to only those where there are numeric ABUND estimates
w_ABUND<-filter(w2, w2$ABUND!="TMTT")

#remove duplicates to have one entry for individual detected
w_ABUND<-distinct(w_ABUND)%>%
  mutate(ABUND=as.numeric(ABUND))

```

##### Sum numerical count data by species/station {-}

``` {r eval=FALSE}

# Consolodate abundance estimates from duplicate stations.Get the total abundance/species/station using the aggregate function
# ~ are the grouping variables while the . represents all other variables to sum  
w_ABUND<-stats::aggregate(formula=ABUND ~SS+DATE+TIME+MAXDUR+MAXDIS+x+y+surveyType+SPECIES+source, data=w_ABUND, FUN=sum)
```


##### Estimate TMTT numerical values {-}

Some of the Wildtrax abundance data is labeled TMTT (too many to count). For each species, I'll convert this to a number by taking the average number of individuals in a group of 3 or more and using that average in place of TMTT.

###### Combine BAM and Wildtrax data {-}

```{r eval=FALSE}
bd<-dplyr::bind_rows(b, w_ABUND)
```


###### Convert bird data to wide format {-}

```{r eval=FALSE}
bd_wide<-tidyr::spread(bd, SPECIES, ABUND, fill=0)
#save(bd_wide, file ="2_pipeline/tmp/bd_wide.rData")
```

###### Calculate mean number of detected individuals of groups of 3 or more per species, and apply to TMTT values. {-}

```{r eval=FALSE}
bx<-bd_wide[-c(1:9)]

#Get mean abundance for each species and apply to corresponding TMTT
library(expss)
bmean<-round(mean_col_if(gt(3), bx), digits = 0)
bm<-as.data.frame(bmean)
bm <- cbind(rownames(bm), data.frame(bm, row.names=NULL))
colnames(bm)<- c("SPECIES","ABUND_TMTT_2")

#IF a species hasn't been detected in groups of 4 or more, convert TMTT to 4
bm[is.na(bm)]<-4


#join TMTT abundance values with the subsetted TMTT Wiltrax data
w_TMTT<-left_join(w_TMTT, bm)

#add TMTT abundance estimates to the abundance column
w_TMTT<-w_TMTT%>%
  mutate(ABUND=(ABUND_TMTT_2))%>%
  dplyr::select(-c(ABUND_TMTT))
```

###### Bind back together the TMTT and numerical abundance subsets of the Wildtrax data {-}

``` {r eval=FALSE}
#bind back together the dataframe
w_f<-w%>%
  filter(ABUND!="TMTT")%>%
  mutate(ABUND=as.numeric(ABUND))%>%
  bind_rows(w_TMTT)%>%
  dplyr::select(-c(ABUND_TMTT_2))%>%
  distinct()

#reaggregate data to get new abundance sums that include the TMTT values
w_f<-aggregate(formula=ABUND ~SS+DATE+TIME+MAXDUR+MAXDIS+x+y+surveyType+SPECIES+source, data=w_f, FUN=sum)

# w_f$x<-as.numeric(w_f$x)
# w_f$y<-as.numeric(w_f$y)
```


### Combine BAM and Wildtrax data {-}

```{r combine_data, eval=FALSE}
bd_a<-bind_rows(b, w_f)

#reorder columns
bd_a<-bd_a[c("SS","x", "y", "DATE", "TIME", "MAXDUR", "MAXDIS", "surveyType", "source", "SPECIES", "ABUND")]

save(bd_a, file = paste0("0_data/manual/bird/bd_a_", Sys.Date(), ".rData"))
```


### Filter birds {-}

Subset data frame so it does not include non-bird defections (e.g. wind, traffic, etc.) and unknown species. 

```{r eval=FALSE, echo=FALSE}

install.packages("remotes")
remotes::install_github("RS-eco/traitdata")
library(traitdata)

bird_alpha<-read.csv("0_data/external/IBP-Alpha-Codes20.csv")

#bl<-bird_lh[c(1, 5:6, 13)]

#Get list of the bird species included in this analyis (extracted from my wide format bird data)
spp<-as.data.frame(unique(bd_a$SPECIES))%>%
 dplyr::rename("SPEC"="unique(bd_a$SPECIES)")

# repalce misused species codes
spp$SPEC[spp$SPEC == 'STSP'] <- 'NESP'
spp$SPEC[spp$SPEC == 'GRAJ'] <- 'CAJA'


# join analysis species list with the species name data
bn<-inner_join(spp, bird_alpha, by="SPEC")%>%
 separate(SCINAME, into = c("Genus", "Species"), sep = " (?=[^ ]+$)")

# removed unidentified speces
bn_1<-bn%>%
 filter(!grepl('Unidentified', COMMONNAME))


# Get total detections by species
#Set minimum detections threshold
bd_wide<-spread(bd_a, SPECIES, ABUND, fill=0)
b<-bd_wide[-c(1:9)]
totDet<-colSums(b !=0)
totDet<-totDet[order(-totDet)]
totDet<-as.data.frame(totDet)
# add common species name
bird_alpha<-read.csv("0_data/external/IBP-Alpha-Codes20.csv")
ba<-bird_alpha[c(2,4)]
totDet<-left_join(rownames_to_column(totDet, "SPEC"), ba, by=c("SPEC"="SPEC"))
totDet<-totDet[c(1,3,2)]
names(totDet)[1]<-"spp"

#save(totDet, file ="2_pipeline/store/totDet_qpad.rData")
save(totDet, file ="2_pipeline/store/totDet.rData")

# set minimum number of detections
nmin<-5
totDet_f<-totDet%>%
  filter(totDet>5)

# Filter bird data based on detections
bn_2<-semi_join(bn_1, totDet_f, by=c("SPEC"="spp"))


# Remove flyover species
# Get other toxonomic info
#t<-trait_glossary
el<-elton_birds  
library(fuzzyjoin)
# el2<-el[c(1, 8:10)]
library(fuzzyjoin)
bn_3<-stringdist_semi_join(bn_2, el, by= c("Genus", "Species"), max_dist=1, ignore_case=TRUE)
bn_4<-stringdist_semi_join(bn_2, el, by= c("COMMONNAME" = "English"), max_dist=1, ignore_case=TRUE)

bn_5<-rbind(bn_3, bn_4)%>%
  distinct()

#check the bird codes that didn't match
bn_6<-anti_join(bn_2, bn_5)

# filter flyover species
bn_7<-bn_5%>%
  left_join(el)%>%
  filter(Family!="Anatidae"&Family!="Pelecanidae"&Family!="Gaviidae"&Family!="Podicipedidae")

bd_traits_full<-bn_7
save(bd_traits_full, file=paste0("0_data/manual/bird/bd_traits_full_", Sys.Date(), ".rData"))


totDet_f_2<-totDet_f%>%
  inner_join(bn_7)%>%
  dplyr::select(-c(SPEC, CONF))%>%
  dplyr::select(c(spp:BLFamilyEnglish))

save(totDet_f_2, file ="2_pipeline/store/totDet_f_2.rData")



save(bd_a, file = paste0("0_data/manual/bird/bd_a_", Sys.Date(), ".rData"))

bd_f<-semi_join(bd_a, totDet_f_2, by=c("SPECIES"="spp"), copy=TRUE)

save(bd_f, file = paste0("0_data/manual/bird/bd_f_", Sys.Date(), ".rData"))
```

### Format 
```{r}
bd_wide<-spread(bd_f, SPECIES, ABUND, fill=0)%>%
  mutate(survey_year=year(DATE))%>%
  group_by(SS, survey_year)%>%
  mutate(n_count=n())%>%
  dplyr::select(c(SS:TIME, survey_year, n_count, MAXDUR:YHBL))

save(bd_wide, file=paste0("0_data/manual/bird/bd_wide", Sys.Date(), ".rData"))
```

### Calculate metrics {-}

#### Calculate abundance {-}

Detentions summed over all repeated visits for each year

```{r eval=FALSE}
x<-bd_wide

# x$DATE<-as.Date(x$DATE)
x$survey_year<-format(as.Date(x$DATE, format="%d/%m/%Y"),"%Y")
x<-x[-c(2:3, 5:11)]
x<-aggregate(. ~SS+survey_year, x, sum)

z<-x[3:ncol(x)]

# remove species with no detections
z<-z[,colSums(z[,c(3:ncol(z))]) > 0]

z = z[,colSums(z) > 0]

z<-cbind(x[1:2], z)

x<-z
```


#### Diversity metrics {-}

``` {r eval=FALSE}
library(vegan)
# richness
richness<-apply(x[-c(1:2)]>0,1,sum)

# Menhinick's index 
#"number of species (n) divided by the square-root of the total number of individuals (N)"
n<-apply(x[-c(1:2)]>0,1,sum)
N <- apply(x[-c(1:2)],1,sum)
menhIndx<-n/sqrt(N)


# Margalef's index 
#The number of species (n) minus 1 divided by the natural logarithm of the total number of individuals (N). 
n<-apply(x[,-c(1:2)]>0,1,sum)
N <- apply(x[,-c(1:2)],1,sum)
margIndx<-(n-1)/log(N)

# Alpha diversity 
# Shannon-Weiner Index 
shan<-diversity(x[-c(1:2)], index="shannon")

# Brillouin Index 
brillouin <- function(x) {
   N <- sum(x)
   (log(factorial(N)) - sum(log(factorial(x))))/N
}
brill<-apply(x[-c(1:2)],1,brillouin)

# Simpson's Index 
simp<-diversity(x[-c(1:2)], index="simpson")

# Evenness 
# Pilou evenness 
S <- apply(x[-c(1:2)]>0,1,sum)
pilou<-diversity(x[-c(1:2)], index="simpson")/log(S)

# Hills ratio 
S <- apply(x[-c(1:2)]>0,1,sum)
hill<-exp(diversity(x[-c(1:2)], index="simpson"))/S

# Combine
bd_div<-data.frame(x[1:2], richness, menhIndx, margIndx, shan, brill, simp, pilou, hill)
save(bd_div, file=paste0("0_data/manual/bird/bd_div", Sys.Date(), ".rData"))

```

-----


#### Functional diversity {-}

Functional traits were extracted from [@EltonTraits2021]

```{r eval=FALSE}
load("0_data/manual/bird/bd_traits_full_2023-02-10.rData")

# Keep only traits of interest

bd_tr<-bd_traits_full%>%
  dplyr::select(c("SPEC", "Diet.Inv", "Diet.Vend",
"Diet.Vect", "Diet.Vfish", "Diet.Vunk",
"Diet.Scav", "Diet.Fruit", "Diet.Nect",
"Diet.Seed", "Diet.PlantO", "Diet.5Cat",
"ForStrat.watbelowsurf", "ForStrat.wataroundsurf", "ForStrat.ground",
"ForStrat.understory", "ForStrat.midhigh", "ForStrat.canopy",
"ForStrat.aerial", "PelagicSpecialist", "Nocturnal",
"BodyMass.Value"))%>%
  arrange(SPEC)

```

**Calculate functional diversity**

Calculate functional diversity metrics using the methods of: 

Laliberté, E.; Legendre, P.; Shipley, B. FD: Measuring Functional Diversity from Multiple Traits, and Other Tools for Functional Ecology. R Package Version 1.0-12. 2014. Available online: <https://cran.r-project.org/web/packages/FD>.

```{r eval=FALSE}
library(FD)

# set species codes as rownames in trait dataframe
traits<- bd_tr[,-1]
rownames(traits) <- bd_tr[,1]

#detection data (detection column names match trait row names)
abund<-x
abund1<-x[-c(1:2)]

#covert dataframe to matrix
abund2<-data.matrix(abund1)

##################################
#Calculate functional diversity metrics with FD:dbFD
fd3<- FD::dbFD(traits, abund2)
#############################################
# bind functional diversity metrics with station data

bd_funcDiv<-cbind(abund[1:2], fd3)
save(bd_funcDiv, file=paste0("0_data/manual/bird/bd_FuncDiv", Sys.Date(), ".rData"))
```

Combine all diversity metrics into single dataframe
```{r}
bd_community<-bd_wide%>%
  dplyr::select(c(SS, survey_year:surveyType))%>%
  distinct()%>%
  inner_join(bd_div)%>%
  left_join(bd_funcDiv)%>%
  dplyr::select(-c(CWM.Diet.Inv:CWM.BodyMass.Value))

save(bd_community, file=paste0("0_data/manual/bird/bd_community", Sys.Date(), ".rData"))
```


### Get XY coordinates {-}

Create spatial object with point count locations.

```{r eval=FALSE}
ss_xy<-bd_wide%>%
  dplyr::select(SS, x, y)%>%
  distinct()

ss_xy<-st_as_sf(ss_xy, coords=c("x","y"), crs=4326)

sx_xy<-st_transform(ss_xy, crs=3400)

save(ss_xy, file="0_data/manual/spatial/bird/ss_xy.rData")
st_write(ss_xy, "0_data/manual/spatial/bird/ss_xy.shp")

```

