```{r setup, include=FALSE, cache=FALSE}
#Set root directory to R project root
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

setwd(rprojroot::find_rstudio_root_file())
```

```{r eval=FALSE}
library(dplyr)
library(readr)
library(data.table)
```

## GEE scripts {.unnumbered}

Bring GEE scripts into the current rProject by cloning the GEE git and copying over the .js files.

```{bash engine.opts='-l', eval=FALSE}
# set directory to clone GEE git into (should be empty)
cd 1_code/GEE

# delete all .js files in directory
rm *.js

# clone gee scripts
git clone https://earthengine.googlesource.com/users/bgcasey/harvest_severity_birds

# add the .js file extention to files
find harvest_severity_birds -type f -not -name "*.*" -exec mv "{}" "{}".js \;

# move .js files up a directory
mv -v harvest_severity_birds/*.js .

# move functions folder up a directory
mv -v harvest_severity_birds/functions/ .

# delete .git folder
rm -r harvest_severity_birds/
```

## GEE CSVs {.unnumbered}

### Landcover metrics {.unnumbered}

```{r eval=FALSE}
gee_metrics<-read_csv("0_data/manual/gee_tables/gee_metrics.csv")

gee_metrics_2<-gee_metrics%>%  
  dplyr::select(-c(histogram, "system:time_start", ".geo", "system:index", "count"))%>%
  dplyr::select(SS, 17:18, 1:7, 9:16)%>%
  dplyr::filter(landcover_yr==srvy_yr|srvy_yr>=2020)%>%
  mutate(landcover_yr_2 = ifelse(srvy_yr >= 2020, 2019, landcover_yr))%>%
  filter(landcover_yr_2==landcover_yr)%>%
  dplyr::select(-landcover_yr)%>%
  dplyr::rename(landcover_yr=landcover_yr_2)


### add latitude
library(sf)

load("0_data/manual/spatial/bird/ss_xy.rData")

ss_xy <- ss_xy %>%
  ungroup() %>%
  dplyr::mutate(lon = sf::st_coordinates(.)[,1],
                lat = sf::st_coordinates(.)[,2])%>%
  as.data.frame()%>%
  dplyr::select(-geometry)%>%
  rename(srvy_yr=survey_year)

gee_metrics_3<-dplyr::left_join(gee_metrics_2, ss_xy, by=c("SS", "srvy_yr"))

gee_landcover<-gee_metrics_3
save(gee_landcover, file="0_data/manual/gee_landcover.rData")
```

### NBR {.unnumbered}

```{r importGEE_csv, eval=FALSE}

filepath<-"0_data/manual/gee_tables/nbr/"

#--- Get list of names for original metric GEE output files
origFiles <- list.files(path=paste0(filepath, "unprocessed/"), pattern="*.csv$", full.names=TRUE, recursive=FALSE)

```

#### Reformat each .csv file {.unnumbered}

```{r reformatGEEcsv, eval=FALSE}

#--- Import data from current file
thisDat <- fread("0_data/manual/gee_tables/HA_Polys_ABMI2021_20220315.csv", data.table = FALSE)
  
#--- Generate list of unique OBJECTID values
OIDs <- sort(unique(thisDat$OBJECTID), decreasing=FALSE)

#--- Dataframe of survey and CAS-FRI info
surv<-unique(thisDat[c(1:4)])

#--- Compile vector of all unique metric values
metricList <- as.character(unique(thisDat$METRIC))
  
  #--- Create column names so that the mean and standard deviation of each metric have columns
fullMetricCols <- list()
  for (n in 1:length(metricList)){
    meanName <- paste0(metricList[n],"_mean")
    stdevName <- paste0(metricList[n],"_stdev")
    fullMetricCols <- c(fullMetricCols,meanName,stdevName)
  }
  
#--- Reformat metric data to create new table
#--------------------------------------------
  
#--- Initiatlize a dataframe, with OBJECTIDs in the first column
outMetTable <- data.frame("OBJECTID"=OIDs)

#--- For each item in metricList, do the following:
for (j in 1:length(metricList)){
    #--- Subset thisDat, selecting rows where the current metric in the list
    #---   is in the METRIC column, but output only the METRIC_MEAN and METRIC_STDEV columns
    colData <- subset(thisDat, METRIC == metricList[j], select = c("OBJECTID","METRIC_MEAN","METRIC_STDEV"))
    colData <- colData[order(colData$OBJECTID),]
    outData <- subset(colData, select = c("METRIC_MEAN","METRIC_STDEV"))
    #--- Extract the corresponding, appropriate column names for metric [j] from fullMetricCols
    metricPos <- which(fullMetricCols == paste0(metricList[j],"_mean"))
    colnames(outData) <- fullMetricCols[c(metricPos,metricPos+1)]
    #--- Add the result to the outMetTable dataframe
    outMetTable <- cbind(outMetTable, outData)
  }

#--- Reformat flag data, and combine with metric data
#----------------------------------------------------
  
#--- Create output data frame
flagData <- data.frame("TOT_PIXELS"=0,"PERC_UNMSKD"=0,"UNMSKD_PIXELS"=0,"MAX_CONNCTDPIX"=0,"PERC_NOHARVEST"=0,"PERC_MULTIDISTB"=0,"PERC_OUTOFRANGE"=0,"PERC_NOREGEN"=0,"PERC_NO5REGEN"=0,"PERC_NO10REGEN"=0,"PERC_NO15REGEN"=0,"PERC_NO20REGEN"=0)
 
#--- List of relevant columns
flagCols <- c("TOT_PIXELS","PERC_UNMSKD","UNMSKD_PIXELS","MAX_CONNCTDPIX","PERC_NOHARVEST","PERC_MULTIDISTB","PERC_OUTOFRANGE","PERC_NOREGEN","PERC_NO5REGEN","PERC_NO10REGEN","PERC_NO15REGEN","PERC_NO20REGEN")

#--- Extract "TOT_PIXELS", "UNMSKD_PIXELS", & other Flag columns for each OBJECTID
for (k in 1:length(OIDs)){
    
  #--- Find first occurrnce of current OBJECTID, extract flag column data,
  #--- and add to flagData data frame
  objRow <- match(OIDs[k], thisDat[,"OBJECTID"])
  objFlags <- thisDat[objRow,flagCols]
  flagData <- rbind(flagData,objFlags)
  }
 
#--- Remove first row (full of zeros)
flagData <- flagData[-1,]

#--- Add flag columns to metric information
outMetTable <- cbind(outMetTable, flagData)

#-- add survey info to metric table
outMetTable_fin <-left_join(outMetTable,surv)
# outMetTable_fin <- outMetTable_fin[, c(1, 48:50, 2:47)]
outMetTable_fin <- outMetTable_fin%>%
dplyr::select(OBJECTID, HFI_ID, uniquID, YEAR, preDistMean_mean:PERC_NO20REGEN)


#--- Write to output file
#------------------------
fwrite(outMetTable_fin, file = "0_data/manual/gee_tables/HA_Polys_ABMI2021_20220315_RFMTTD.csv")

#--- Create new data frame for further additions, and modifications
fullData <- outMetTable_fin[order(outMetTable_fin$OBJECTID),]
str(fullData)
save(fullData, file=paste0("0_data/manual/gee_tables/fulDataNBR_", Sys.Date(), ".rData"))
```

#### Calculate confidence scores and add to data frame {.unnumbered}

Calculate relative confidence scores for each HA polygon based on various flag and metric results, using table found in "JHird_ABMI_HArecovery_overview&prelimStats_20191004.pdf",where 0 = Very Low, 1=Low, 2=Medium-Low, 3=Medium, 4=Medium-High, 5=High, and 6=Very High

```{r calculate_confidence_scores, eval=FALSE}

#--- List of columns to use in calculations
sizeCols <- c("OBJECTID","TOT_PIXELS","UNMSKD_PIXELS","PERC_UNMSKD","MAX_CONNCTDPIX","yod_stdev",
              "lengthDistb_stdev", "totDistb_stdev","totRegen_stdev","yrTo80_stdev", "regen5yr_stdev")

#--- Extract selected columns
confTable <- fullData[sizeCols]

#--- Set up data frame for calculations
confTable <- cbind(confTable,"sizeConf"=0,"availPixConf"=0,"contgPixConf"=0,"yodConf"=0,
                   "t2regenConf"=0,"distbConf"=0,"regenConf"=0, "y2r80Conf"=0, "reg5yrConf"=0)


#--- Calculate: value of "sizeConf"
#----------------------------------

#--- Where total pixel count is < 1, sizeConf=0
nolt1 <- which(confTable$TOT_PIXELS < 1)
confTable[nolt1, "sizeConf"] <- 0

#--- where count is >=1 & <11, sizeConf=1
nogte1 <- which(confTable$TOT_PIXELS >= 1 &
                  confTable$TOT_PIXELS < 11)
confTable[nogte1, "sizeConf"] <- 1

#--- where count is >=11 & <20, sizeConf=2
nogte11 <- which(confTable$TOT_PIXELS >= 11 &
                   confTable$TOT_PIXELS < 20)
confTable[nogte11, "sizeConf"] <- 2

#--- where count is >=20 & <30, sizeConf=3
nogte20 <- which(confTable$TOT_PIXELS >= 20 &
                   confTable$TOT_PIXELS < 30)
confTable[nogte20, "sizeConf"] <- 3

#--- where count is >=30 & <100, sizeConf=4
nogte30 <- which(confTable$TOT_PIXELS >= 30 &
                   confTable$TOT_PIXELS < 100)
confTable[nogte30, "sizeConf"] <- 4

#--- where count is >=100 & <200, sizeConf=5
nogte100 <- which(confTable$TOT_PIXELS >= 100 &
                    confTable$TOT_PIXELS < 200)
confTable[nogte100, "sizeConf"] <- 5

#--- where count is >=100 & <200, sizeConf=5
nogte200 <- which(confTable$TOT_PIXELS >= 200)
confTable[nogte200, "sizeConf"] <- 6


#--- Calculate: value of "availPixConf"
#--------------------------------------

#--- Where percentage of unmasked pixels is < 50%, availPixConf=0
availLt50 <- which(confTable$PERC_UNMSKD < 50.0)
confTable[availLt50, "availPixConf"] <- 0

#--- where percentage is >=50% & <60%, availPixConf=1
availgte50 <- which(confTable$PERC_UNMSKD >= 50.0 &
                      confTable$PERC_UNMSKD < 60.0)
confTable[availgte50, "availPixConf"] <- 1

#--- where percentage is >=60% & <70%, availPixConf=2
availgte60 <- which(confTable$PERC_UNMSKD >= 60.0 &
                      confTable$PERC_UNMSKD < 70.0)
confTable[availgte60, "availPixConf"] <- 2

#--- where percentage is >=70% & <80%, availPixConf=3
availgte70 <- which(confTable$PERC_UNMSKD >= 70.0 &
                      confTable$PERC_UNMSKD < 80.0)
confTable[availgte70, "availPixConf"] <- 3

#--- where percentage is >=80% & <90%, availPixConf=4
availgte80 <- which(confTable$PERC_UNMSKD >= 80.0 &
                      confTable$PERC_UNMSKD < 90.0)
confTable[availgte80, "availPixConf"] <- 4

#--- where percentage is >=90% & <100%, availPixConf=5
availgte90 <- which(confTable$PERC_UNMSKD >= 90.0 &
                      confTable$PERC_UNMSKD < 100.0)
confTable[availgte90, "availPixConf"] <- 5

#--- where percentage is 100%, availPixConf=6
avail100 <- which(confTable$PERC_UNMSKD == 100.0)
confTable[avail100, "availPixConf"] <- 6


#--- Calculate: value of "contgPixConf"
#--------------------------------------

#--- Where number of contiguous pixels is < 5, contgPixConf=0
ctglt0 <- which(confTable$MAX_CONNCTDPIX <= 0)
confTable[ctglt0, "contgPixConf"] <- 0

#--- Where number of contiguous pixels is >= 5 & < 11, contgPixConf=1
ctglte2 <- which(confTable$MAX_CONNCTDPIX > 0 &
                   confTable$MAX_CONNCTDPIX <= 2)
confTable[ctglte2, "contgPixConf"] <- 1

#--- Where number of contiguous pixels is >= 5 & < 11, contgPixConf=2
ctglte4 <- which(confTable$MAX_CONNCTDPIX > 2 &
                   confTable$MAX_CONNCTDPIX <= 4)
confTable[ctglte4, "contgPixConf"] <- 2

#--- Where number of contiguous pixels is >= 5 & < 11, contgPixConf=3
ctglte6 <- which(confTable$MAX_CONNCTDPIX > 4 &
                   confTable$MAX_CONNCTDPIX <= 6)
confTable[ctglte6, "contgPixConf"] <- 3

#--- Where number of contiguous pixels is >= 5 & < 11, contgPixConf=4
ctglte8 <- which(confTable$MAX_CONNCTDPIX > 6 &
                   confTable$MAX_CONNCTDPIX <= 8)
confTable[ctglte8, "contgPixConf"] <- 4

#--- Where number of contiguous pixels is >= 5 & < 11, contgPixConf=5
ctglte10 <- which(confTable$MAX_CONNCTDPIX > 8 &
                    confTable$MAX_CONNCTDPIX <= 10)
confTable[ctglte10, "contgPixConf"] <- 5

#--- Where number of contiguous pixels is >= 11 & < 15, contgPixConf=2
ctgGte11 <- which(confTable$MAX_CONNCTDPIX >= 11)
confTable[ctgGte11, "contgPixConf"] <- 6


#--- Calculate: value of "yodConf"
#---------------------------------

#--- Where std dev of yod is >= 3 (years), yodConf=0
yodgte3 <- which(confTable$yod_stdev >= 3)
confTable[yodgte3, "yodConf"] <- 0

#--- Where std dev of yod is >= 2.5 & < 3, yodConf=1
yodgte25 <- which(confTable$yod_stdev >= 2.5 &
                    confTable$yod_stdev < 3)
confTable[yodgte25, "yodConf"] <- 1

#--- Where std dev of yod is >= 2 & < 2.5, yodConf=2
yodgte2 <- which(confTable$yod_stdev >= 2 &
                   confTable$yod_stdev < 2.5)
confTable[yodgte2, "yodConf"] <- 2

#--- Where std dev of yod is >= 1.5 & < 2, yodConf=3
yodgte15 <- which(confTable$yod_stdev >= 1.5 &
                    confTable$yod_stdev < 2)
confTable[yodgte15, "yodConf"] <- 3

#--- Where std dev of yod is >= 1 & < 1.5, yodConf=4
yodgte1 <- which(confTable$yod_stdev >= 1  &
                   confTable$yod_stdev < 1.5)
confTable[yodgte1, "yodConf"] <- 4

#--- Where std dev of yod is >= 0.5 & < 1, yodConf=5
yodgte05 <- which(confTable$yod_stdev >= 0.5 &
                    confTable$yod_stdev < 1)
confTable[yodgte05, "yodConf"] <- 5

#--- Where std dev of yod is < 0.5, yodConf=6
yodlt05 <- which(confTable$yod_stdev < 0.5)
confTable[yodlt05, "yodConf"] <- 6


#--- Calculate: value of "t2regenConf"
#-------------------------------------

#--- Where std dev of lengthDistb is >= 3 (years), t2regenConf=0
t2reggte3 <- which(confTable$lengthDistb_stdev >= 3)
confTable[t2reggte3, "t2regenConf"] <- 0

#--- Where std dev of lengthDistb is >= 2 & < 3 (years), t2regenConf=1
t2reggte2 <- which(confTable$lengthDistb_stdev >= 2 &
                     confTable$lengthDistb_stdev < 3)
confTable[t2reggte2, "t2regenConf"] <- 1

#--- Where std dev of lengthDistb is >= 1.5 & < 2 (years), t2regenConf=2
t2reggte15 <- which(confTable$lengthDistb_stdev >= 1.5 &
                      confTable$lengthDistb_stdev < 2)
confTable[t2reggte15, "t2regenConf"] <- 2

#--- Where std dev of lengthDistb is >= 1 & < 1.5 (years), t2regenConf=3
t2reggte1 <- which(confTable$lengthDistb_stdev >= 1 &
                     confTable$lengthDistb_stdev < 1.5)
confTable[t2reggte1, "t2regenConf"] <- 3

#--- Where std dev of lengthDistb is >= 0.75 & < 1 (years), t2regenConf=4
t2reggte075 <- which(confTable$lengthDistb_stdev >= 0.75 &
                       confTable$lengthDistb_stdev < 1)
confTable[t2reggte075, "t2regenConf"] <- 4

#--- Where std dev of lengthDistb is >= 0.25 & < 0.75 (years), t2regenConf=5
t2reggte025 <- which(confTable$lengthDistb_stdev >= 0.25 &
                       confTable$lengthDistb_stdev < 0.75)
confTable[t2reggte025, "t2regenConf"] <- 5

#--- Where std dev of lengthDistb is > 0.25 (years), t2regenConf=6
t2reglt025 <- which(confTable$lengthDistb_stdev < 0.25)
confTable[t2reglt025, "t2regenConf"] <- 6


#--- Calculate: value of "distbConf"
#-----------------------------------

#--- Where std dev of totDistb is >= 200 (NBR units), totDistbConf=0
totDtbgte200 <- which(confTable$totDistb_stdev >= 200)
confTable[totDtbgte200, "distbConf"] <- 0

#--- Where std dev of totDistb is >= 150 & < 200 (NBR units), totDistbConf=1
totDtbgte150 <- which(confTable$totDistb_stdev >= 150 &
                        confTable$totDistb_stdev < 200)
confTable[totDtbgte150, "distbConf"] <- 1

#--- Where std dev of totDistb is >= 125 & < 150 (NBR units), totDistbConf=2
totDtbgte125 <- which(confTable$totDistb_stdev >= 125 &
                        confTable$totDistb_stdev < 150)
confTable[totDtbgte125, "distbConf"] <- 2

#--- Where std dev of totDistb is >= 115 & < 125 (NBR units), totDistbConf=3
totDtbgte115 <- which(confTable$totDistb_stdev >= 115 &
                        confTable$totDistb_stdev < 125)
confTable[totDtbgte115, "distbConf"] <- 3

#--- Where std dev of totDistb is >= 100 & < 115 (NBR units), totDistbConf=4
totDtbgte100 <- which(confTable$totDistb_stdev >= 100 &
                        confTable$totDistb_stdev < 115)
confTable[totDtbgte100, "distbConf"] <- 4

#--- Where std dev of totDistb is >= 75 & < 100 (NBR units), totDistbConf=5
totDtbgte75 <- which(confTable$totDistb_stdev >= 75 &
                       confTable$totDistb_stdev < 100)
confTable[totDtbgte75, "distbConf"] <- 5

#--- Where std dev of totDistb is < 75 (NBR units), totDistbConf=6
totDtblt75 <- which(confTable$totDistb_stdev < 75)
confTable[totDtblt75, "distbConf"] <- 6


#--- Calculate: value of "regenConf"
#-----------------------------------

#--- Where std dev of totRegen is >= 30 (precent regeneration), totRegnConf=0
totReggte30 <- which(confTable$totRegen_stdev >= 30)
confTable[totReggte30, "regenConf"] <- 0

#--- Where std dev of totRegen is >= 25 & < 30 (precent regeneration), totRegnConf=1
totReggte25 <- which(confTable$totRegen_stdev >= 25 &
                       confTable$totRegen_stdev < 30)
confTable[totReggte25, "regenConf"] <- 1

#--- Where std dev of totRegen is >= 20 & < 25 (precent regeneration), totRegnConf=2
totReggte20 <- which(confTable$totRegen_stdev >= 20 &
                       confTable$totRegen_stdev < 25)
confTable[totReggte20, "regenConf"] <- 2

#--- Where std dev of totRegen is >= 15 & < 20 (precent regeneration), totRegnConf=3
totReggte15 <- which(confTable$totRegen_stdev >= 15 &
                       confTable$totRegen_stdev < 20)
confTable[totReggte15, "regenConf"] <- 3

#--- Where std dev of totRegen is >= 10 & < 15 (precent regeneration), totRegnConf=4
totReggte10 <- which(confTable$totRegen_stdev >= 10 &
                       confTable$totRegen_stdev < 15)
confTable[totReggte10, "regenConf"] <- 4

#--- Where std dev of totRegen is >= 6 & < 10 (precent regeneration), totRegnConf=5
totReggte6 <- which(confTable$totRegen_stdev >= 6 &
                      confTable$totRegen_stdev < 10)
confTable[totReggte6, "regenConf"] <- 5

#--- Where std dev of totRegen is < 6 (precent regeneration), totRegnConf=6
totReglt6 <- which(confTable$totRegen_stdev < 6)
confTable[totReglt6, "regenConf"] <- 6


#--- Calculate confidence scores from Y2R80 std dev metric
#---------------------------------------------------------

# yrTo80_stdev::
# ----------------
#  max: 12.5
#  min: 0
#  mean: 2.225699
#  median: 2.061553
#  Stdev: 1.4598

#--- Where std dev of Y2R80 is >= 3.5, confidence is very low
gte3.5 <- which(confTable$yrTo80_stdev >= 3.5)
confTable[gte3.5, "y2r80Conf"] <- 0

#--- Where std dev of Y2R80 is >= 3 & < 3.5, confidence is low
gte3 <- which(confTable$yrTo80_stdev >= 3 &
                confTable$yrTo80_stdev < 3.5)
confTable[gte3, "y2r80Conf"] <- 1

#--- Where std dev of Y2R80 is >= 2.5 & < 3, confidence is medium-low
gte2.5 <- which(confTable$yrTo80_stdev >= 2.5 &
                  confTable$yrTo80_stdev < 3)
confTable[gte2.5, "y2r80Conf"] <- 2

#--- Where std dev of Y2R80 is >= 2 & < 2.5, confidence is medium
gte2 <- which(confTable$yrTo80_stdev >= 2 &
                confTable$yrTo80_stdev < 2.5)
confTable[gte2, "y2r80Conf"] <- 3

#--- Where std dev of Y2R80 is >= 1.5 & < 2, confidence is medium-high
gte1.5 <- which(confTable$yrTo80_stdev >= 1.5 &
                  confTable$yrTo80_stdev < 2)
confTable[gte1.5, "y2r80Conf"] <- 4

#--- Where std dev of Y2R80 is >= 0.5 & < 1.5, confidence is high
gte05 <- which(confTable$yrTo80_stdev >= 0.5 &
                 confTable$yrTo80_stdev < 1.5)
confTable[gte05, "y2r80Conf"] <- 5

#--- Where std dev of Y2R80 is < 0.5, confidence is very high
lt05 <- which(confTable$yrTo80_stdev < 0.5)
confTable[lt05, "y2r80Conf"] <- 6


#--- Calculate confidence scores from Y2R80 std dev metric
#---------------------------------------------------------
#** ADDED IN CONF SCORES FOR VARIABILITY IN 5-YR REGEN:: (09-01-2020)

# hist(inData$regen5yr_stdev)

# regen5yr_stdev::
# ----------------
#  max: 91.202222
#  min: 0
#  mean: 14.61652
#  median: 14.24198
#  Stdev: 7.407865

# > 30: very low
# 25-30: low
# 20-25: med-low
# 15-20: med
# 10-15: med high
# 5-10: high
# < 5: very high

#--- Where std dev of 5yr Regen is >= 30, confidence is very low
yr5gt30 <- which(confTable$regen5yr_stdev >= 30)
confTable[yr5gt30, "reg5yrConf"] <- 0

#--- Where std dev of 5yr Regen is >= 25 & < 30, confidence is low
yr5gte25 <- which(confTable$regen5yr_stdev >= 25 &
                confTable$regen5yr_stdev < 30)
confTable[yr5gte25, "reg5yrConf"] <- 1

#--- Where std dev of 5yr Regen is >= 20 & < 25, confidence is med-low
yr5gte20 <- which(confTable$regen5yr_stdev >= 20 &
                    confTable$regen5yr_stdev < 25)
confTable[yr5gte20, "reg5yrConf"] <- 2

#--- Where std dev of 5yr Regen is >= 15 & < 20, confidence is medium
yr5gte15 <- which(confTable$regen5yr_stdev >= 15 &
                    confTable$regen5yr_stdev < 20)
confTable[yr5gte15, "reg5yrConf"] <- 3

#--- Where std dev of 5yr Regen is >= 10 & < 15, confidence is med-high
yr5gte10 <- which(confTable$regen5yr_stdev >= 10 &
                    confTable$regen5yr_stdev < 15)
confTable[yr5gte10, "reg5yrConf"] <- 4

#--- Where std dev of 5yr Regen is >= 5 & < 10, confidence is high
yr5gte5 <- which(confTable$regen5yr_stdev >= 5 &
                    confTable$regen5yr_stdev < 10)
confTable[yr5gte5, "reg5yrConf"] <- 5

#--- Where std dev of 5yr Regen is < 5, confidence is very high
yr5lt5 <- which(confTable$regen5yr_stdev < 5)
confTable[yr5lt5, "reg5yrConf"] <- 6



#--- Add sum and mean of confidence scores, to compare two types of overall scores
#--- -----------------------------------------------------------------------------

#--- Sum calculated confidence scores for each object, and place into 'sumConf' column
confTable$sumConf <- apply(confTable[,c("sizeConf", "availPixConf", "contgPixConf", "yodConf",
                                        "t2regenConf", "distbConf", "regenConf", "y2r80Conf", "reg5yrConf")], 1,
                           function(x) sum(x))

#--- Reorder fullData and confTable to ensure they're in the same order
fullData <- fullData[order(fullData$OBJECTID),]
confTable <- confTable[order(confTable$OBJECTID),]

# #--- Plot to make sure they all line up
# plot(fullData$OBJECTID, confTable$OBJECTID)

#--- Extract confidence score columns from confTable
selConfTableCols <- subset(confTable, select = c("sizeConf", "availPixConf", "contgPixConf", "yodConf",
                                                 "t2regenConf", "distbConf", "regenConf", "y2r80Conf",
                                                 "reg5yrConf", "sumConf"))

#--- Combine fullData with calculated confidence score columns
finalFullTable <- cbind(fullData, selConfTableCols)

str(finalFullTable) #--- 172606 obs. of 55 variables



#------------------------------- -------------------------------------------------------------
#--- Output full data set to CSV
#--------------------------------------------------------------------------------------------

save(finalFullTable, file="0_data/manual/gee_tables/finalFullTable.rData")
#--- Write to csv
fwrite(finalFullTable, file=paste0("0_data/manual/gee_tables/NBR_allMets_finalFullTable_", Sys.Date(), ".rData"))

```

#### Flag inappropriate, low-confidence, and/or irrelevant records {.unnumbered}

```{r cleanGEEdata, eval=FALSE}
load("0_data/manual/gee_tables/finalFullTable.rData")
##--- Create new data frame for cleaning
cleanData <- finalFullTable
dim(cleanData) #1671

#--- Remove records based on NA values, numbers of pixels, and % of HA unmasked::
#--------------------------------------------------------------------------------

# #--- Remove rows with NA values
# length(which(is.na(cleanData$preDistMean_mean))) #--- n = 7468 (rows with NA values)
# cleanData <- cleanData[which(!is.na(cleanData$preDistMean_mean)),]
# dim(cleanData) #--- n = 4571  obs.
# 
# cleanData_na<-cleanData
# 
# save(cleanData_na, file="2_pipeline/store/NBR_clean_NA_in")

#--- Remove rows/data records wherein >50% of pixels are flagged and masked out
length(which(cleanData$PERC_UNMSKD < 20)) #--- n = 15792
cleanData <- cleanData[which(cleanData$PERC_UNMSKD >= 20),]
dim(cleanData) #--- n = 2280 obs.

#--- Remove rows with < 9 total pixels
length(which(cleanData$UNMSKD_PIXELS < 9)) #--- n = 37804 (rows total available pixels < 9)
cleanData <- cleanData[which(cleanData$UNMSKD_PIXELS >= 5),]
dim(cleanData) #--- n = 4168 obs.

#--- Examine how many rows with no. connected pix < 9 and < 11
length(which(cleanData$MAX_CONNCTDPIX < 9)) #--- n = 3001
length(which(cleanData$MAX_CONNCTDPIX < 11)) #--- n = 4364
cleanData <- cleanData[which(cleanData$MAX_CONNCTDPIX >= 5),]
dim(cleanData) #3535

# #--- Remove values for 10-yr, 15-yr, and 20-yr regen where not appropriate::
# #---------------------------------------------------------------------------
# 
# #---  Set all 20-yr, 15-yr, and 10-yr regen to NA where <50% of pixels in a
# #---    harvest area are available to calculate these
# length(which(cleanData$PERC_NO20REGEN > 50.0)) #--- n = 50017
# no20yrRows <- which(cleanData$PERC_NO20REGEN > 50.0)
# cleanData[no20yrRows, c("regen20yr_mean","regen20yr_stdev")] <- NA
# 
# head(cleanData[which(cleanData$PERC_NO20REGEN > 50.0),c("OBJECTID","PERC_NO20REGEN","regen20yr_mean","regen20yr_stdev")], 20)
# 
# length(which(cleanData$PERC_NO15REGEN > 50.0)) #--- n = 31500
# no15yrRows <- which(cleanData$PERC_NO15REGEN > 50.0)
# cleanData[no15yrRows, c("regen15yr_mean","regen15yr_stdev")] <- NA
# 
# head(cleanData[which(cleanData$PERC_NO15REGEN > 50.0),c("OBJECTID","PERC_NO15REGEN","regen15yr_mean","regen15yr_stdev")], 20)
# 
# length(which(cleanData$PERC_NO10REGEN > 50.0)) #--- n = 13817
# no10yrRows <- which(cleanData$PERC_NO10REGEN > 50.0)
# cleanData[no10yrRows, c("regen10yr_mean","regen10yr_stdev")] <- NA
# 
# head(cleanData[which(cleanData$PERC_NO10REGEN > 50.0),c("OBJECTID","PERC_NO10REGEN","regen10yr_mean","regen10yr_stdev")], 20)
# 
# length(which(cleanData$PERC_NO5REGEN > 50.0)) #--- n = 0
# no5yrRows <- which(cleanData$PERC_NO5REGEN > 50.0)
# cleanData[no5yrRows, c("regen5yr_mean","regen5yr_stdev")] <- NA

#--- Remove records based on low confidence scores::
#---------------------------------------------------

#--- Examine low-confidence data records
head(cleanData[,c(1,grep("Conf",colnames(cleanData)))],50)
head(cleanData[order(cleanData$sumConf),c(1,grep("Conf",colnames(cleanData)))], 50)

dim(cleanData[which(cleanData$yodConf < 4),])   #n = 6,084
dim(cleanData[which(cleanData$distbConf < 4),]) #n = 17,375
dim(cleanData[which(cleanData$regenConf < 4),]) #n = 25,143
dim(cleanData[which(cleanData$y2r80Conf < 4),]) #n = 41,329

dim(cleanData[which(cleanData$sumConf <= 20),]) #n = 128
dim(cleanData[which(cleanData$sumConf <= 22),]) #n = 280
dim(cleanData[which(cleanData$sumConf <= 25),]) #n = 876
dim(cleanData[which(cleanData$sumConf <= 30),]) #n = 4352

hist(cleanData$sumConf)
meanConfScr <- mean(cleanData$sumConf) #mean = 32.88713
meanConfScr
sdConfScr <- sd(cleanData$sumConf)   #sd = 8.636413
sdConfScr

sd2below <- meanConfScr - (2 * sdConfScr)
sd2below #2 stdev below mean = 15.6143
sd3below <- meanConfScr - (3 * sdConfScr)
sd3below #3 stdev below mean = 6.9

dim(cleanData[which(cleanData$sumConf <= 6.9 |
                    cleanData$yodConf < 4),]) #n = 6121

#--- Remove rows with < 4 as a yodConf (year of harvest confidence score)
cleanData <- cleanData[which(cleanData$yodConf >=4),]
dim(cleanData) #n = 66,204

min(cleanData$sumConf) #min = 18
head(cleanData[order(cleanData$sumConf),c(1,grep("Conf",colnames(cleanData)))], 50)
hist(cleanData$sumConf)

#--- Remove rows with < 24 as a total confidence score
cleanData <- cleanData[which(cleanData$sumConf >= 6.9),]
dim(cleanData) #n = 1841

str(cleanData)

#------------------------
#Combine filtered and unfiltered data add a column for data that categroizes data by data I'm confident in and data that I'm not confident in
#-------------------------

t<-anti_join(finalFullTable, cleanData,  c("OBJECTID", "HFI_ID", "YEAR"))%>%
  mutate(flag_pixels="y")
dim(t) #2730

cleanData$flag_pixels="n"

t$highConf="n"
cleanData$highConf="y"

nbr_flagData<-rbind(cleanData,t)

save(nbr_flagData, file="0_data/manual/gee_tables/finalFullTable_flag.rData")
```
